Study locations

### 2023-09-25 Scripts/1_Visualisation/Map_study_locations.Rmd
Organising files

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE}
library(gtools) #Library that allows to sort files by numerical order
library(tidyverse)
library(sf)
#Read all files with their paths
files <- dir("../Data/Clean_data", pattern="*.rds", full.names=T)
files <- mixedsort(files)

@@

#Read all file names
file_names <- dir("../Data/Clean_data", pattern="*.rds", full.names=F)
file_names <- mixedsort(file_names)

>>>>

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE}
library(gtools) #Library that allows to sort files by numerical order
library(tidyverse)
library(sf)
#Read all files with their paths
files <- dir("../../Data/Clean_data", pattern="*.rds", full.names=T)
files <- mixedsort(files)

@@

#Read all file names
file_names <- dir("../../Data/Clean_data", pattern="*.rds", full.names=F)
file_names <- mixedsort(file_names)
